Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-24 edubots_surveys.Rnw
adds the question and section/results for RQ3 refs #16
Eliminates sweave
Adds as code #16 :zap:
Also corresponding to #3

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community. 
% Antonio - En realidad, la comunidad afectada incluiría también a los estudiates, ¿no?
% Por cierto, quizá también se podrían incluir aqui las encuestas pasadas a los estudiantes. No son las mismas preguntas, pero van en una línea similar. Quizá tuviesen cabida y le darían 
% más enjundia al estudio. ;)
In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching. Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
\end{abstract}

@@

@@

% Maybe move it to a different place later
Given the potential advantages that chatbots could bring to the classroom, as a previous step, we have performed a survey to 300 teachers asking about their attitudes towards the use of chatbots in their classes. We analyse in this work their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 -  Which kind of chatbots would teachers find useful in their classes?? }

\item{ RQ3 - Regarding technology acceptance, are there any differences regarding age, gender, or years of experience in Education? }
\item{ RQ4 - } 
\end{itemize}

@@

@@

\section*{Acknowledgements}

>>>>

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community. 
% Antonio - En realidad, la comunidad afectada incluiría también a los estudiates, ¿no?
% Por cierto, quizá también se podrían incluir aqui las encuestas pasadas a los estudiantes. No son las mismas preguntas, pero van en una línea similar. Quizá tuviesen cabida y le darían 
% más enjundia al estudio. ;)
% They are not part of this paper, Antonio. Also: write in English - JJ
In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching. Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
\end{abstract}

@@

<<setup, echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)

data <- read.csv("data/survey-student-interaction-pilot-3-2021-EN.csv")
@

@@

% Maybe move it to a different place later
Given the potential advantages that chatbots could bring to the classroom, as a previous step, we have performed a survey to 300 teachers asking about their attitudes towards the use of chatbots in their classes. We analyse in this work their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }

\end{itemize}

@@

\subsection{RQ2 - Which kind of interaction do teachers prefer with their students?}

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.33\textwidth}
	    \centering
<<gender_synch, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Gender)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Gender, levels=c('Female','Male','PNTS'))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/gender_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.33\textwidth}
	    \centering
<<age_synch, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Age)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Age) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@
% 	    \includegraphics[width=\textwidth]{figures/age_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.35\textwidth}
	    \centering
<<experience_sync, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Experience)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~Experience) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/experience_synch.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.6\textwidth}
	    \centering
<<discipline_synch, echo=FALSE>>=
ggplot(data, aes(x = Interaction.Synchrony..or.not., group = Discipline)) + geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count", show.legend = FALSE) + scale_y_continuous(labels=scales::percent) + ylab("relative frequencies") + facet_grid(~factor(Discipline, levels=c('Biomedicine','Humanities','Social Sciences', "Sciences", "Tech/Engineering","No"))) + theme(axis.title.y=element_blank(), axis.title.x=element_blank())
@

% 	    \includegraphics[width=\textwidth]{figures/discipline_synch.pdf}
    \end{minipage}
\end{center}
    \caption{Synchronous or asynchronous interaction.}
\label{figure:chatbots_synch}
\end{figure}

@@

%This section is repeated
%\section*{Acknowledgements}
